Real-Time Application of Activity Classification from Body-Worn Accelerometers

### 2016-06-05 notes/paper/paper.tex
Added some words for the performance results.

The training module, like the pre-processing module, does not need to be in real time.
This algorithm is the most demanding on computational resources and is rarely ran so this can be performed on a smart phone or tablet.
The purpose of the training module is to derive the reference signal to be used on the micro-controller for real-time processing.
The training process uses the same algorithm kernels as the activity classification.
%
\section{Results}
%
ROC curves, timing results?, flop counts.
\begin{figure}[!tbp]
\RawFloats
  \centering
     \begin{minipage}[b]{0.45\textwidth}
        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
     \end{minipage}
     \hfill
     \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
     \end{minipage}
\end{figure}
%\FloatBarrier
reference to figure \ref{ROC_walk_to_run_fig}
%
\section{Conclusion}
conclusion text.
%
\appendices
%
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
%
\bibliographystyle{plain}
\bibliography{reference}
\end{document}

>>>>

The training module, like the pre-processing module, does not need to be in real time.
This algorithm is the most demanding on computational resources and is rarely ran so this can be performed on a smart phone or tablet.
The purpose of the training module is to derive the reference signal to be used on the micro-controller for real-time processing.
The training process uses the same algorithm kernels as the activity classification.
%
\section{Matched-Filter Performance}
%
To demonstrate how effective the matched-filter is for classification, walking, jogging, and bicycling data has been collected from a single individual. One instance of walking data has been used to train the classifier on and a seperate instance of walking data has been used for comparison. Figure \ref{ROC_walk_to_run_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_bike_fig} shows the comparison to bicycling. Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from for bicycling.
\begin{figure}[!tbp]
\RawFloats
  \centering
     \begin{minipage}[b]{0.45\textwidth}
        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
     \end{minipage}
     \hfill
     \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
     \end{minipage}
\end{figure}
%\FloatBarrier
reference to figure \ref{ROC_walk_to_run_fig}
%
\section{Conclusion}
conclusion text.
%
\appendices
%
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
%
\bibliographystyle{plain}
\bibliography{reference}
\end{document}
